---
title: '10.10'
output:
  html_document:
    df_print: paged
---

##a) Generate data set
```{r}
set.seed(2)
dt <- rbind(matrix(rnorm(20*50, mean = 0), nrow = 20), matrix(rnorm(20*50, mean=1), nrow = 20), matrix(rnorm(20*50, mean=2), nrow = 20))
```

##b) PCA
```{r}
pca =prcomp(dt , scale =TRUE)
plot(pca$x[, 1:2], col =c(rep(1,20), rep(2,20), rep(3,20)), pch = 20)
```

##c) K-means clustering K = 3 
```{r}
km.3 =kmeans(dt,3,nstart=20)
true_class = c(rep(1,20), rep(2,20), rep(3,20))
table(km.3$cluster, true_class)
```
The clusters obtained in K-means clustering match with the true class labels.

##d) K-means clustering K = 2
```{r}
km.2 =kmeans(dt,2,nstart=20)
km.2$cluster
```
Now two classes are combined.

##e) K-means clustering K = 4
```{r}
km.4 =kmeans(dt,4,nstart=20)
km.4$cluster
```
One of the classes is splitted in two.

##f) K-means clustering K = 3 on first two principal component score vectors
```{r}
km.pca = kmeans(pca$x[,1:2], 3, nstart = 20)
table(km.pca$cluster, true_class)
```
Similarly, the clusters obtained in K-means clustering match with the true class labels.

##g) K-means clustering K = 3 on scaled data
```{r}
km.3.scaled = kmeans(scale(dt), 3, nstart=20)
table(km.3.scaled$cluster, true_class)
```
Similarly, the clusters obtained in K-means clustering match with the true class labels. Scaling does not change the results.
