---
title: '10.9'
output:
  html_document:
    df_print: paged
---

```{r}
library(ISLR)
library(data.table)
dt <- data.table(USArrests)
```

##a Hierarchical clustering with complete linkage and Euclidean distance
```{r}
hc.complete = hclust(dist(dt), method ="complete")
plot(hc.complete ,main="Complete Linkage", xlab="", sub ="", cex =.9)
```

##b
Cut the dendrogram at a height that results in three distinct clusters. Which states belong to which clusters?
```{r}
hc.3clusters=cutree(hc.complete, 3)
```

##c
Hierarchically cluster the states using complete linkage and Euclidean distance, after scaling the variables to have standard deviation one.
```{r}
dt2 <- scale(data.table(USArrests))
hc.complete2 = hclust(dist(dt2), method ="complete")
plot(hc.complete2,main="Complete Linkage", xlab="", sub ="", cex =.9)
```

##d
What effect does scaling the variables have on the hierarchical clustering obtained? In your opinion, should the variables be scaled before the inter-observation dissimilarities are computed? Provide a justification for your answer.

```{r}
hc.3clusters2 = cutree(hc.complete2, 3)
table(hc.3clusters,hc.3clusters2)
```
Scaling the variables affect the clusters obtained although the trees are somewhat similar. The variables should be scaled beforehand because the data measures have different units.