---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

#9.4

```{r}
library(e1071)
library(data.table)
```

First, we create two-class data set with 100 observations and
two features in which there is a visible but non-linear separation between
the two classes. We also create training and test data.
```{r}
set.seed(1)
x <- rnorm(100)
y <- 4 * x^2 + 1 + rnorm(100)
class <- sample(100, 50)
y[class] <- y[class] + 3
y[-class] <- y[-class] - 3
plot(x[class], y[class], col = "red", xlab = "X", ylab = "Y", ylim = c(-6, 30))
points(x[-class], y[-class], col = "blue")

z <- rep(-1, 100)
z[class] <- 1
dt <- data.frame(x = x, y = y, z = as.factor(z))
train <- sample(100, 50)
dt.train <- dt[train, ]
dt.test <- dt[-train, ]
```

Then, we fit the support vector classifier on the training data and its training error rate is 12%
```{r}
svc = svm(z~., data=dt.train, kernel ="linear", cost =10)
plot(svc,dt.train)
svc.pred = predict(svc,dt.train)
table(svc.pred,dt.train$z)
```

Next, we have the support vector machine with a polynomial kernel (with degree 2) and its training error rate is 42%.
```{r}
svmpoly = svm(z~.,data=dt.train,kernel="polynomial",cost=10)
plot(svmpoly,dt.train)
svmpoly.pred = predict(svmpoly,dt.train)
table(svmpoly.pred,dt.train$z)
```

And the support vector machine with a radial kernel and its training error rate is 0%.
```{r}
svmrad = svm(z~.,data=dt.train,kernel="radial",gamma=1,cost=10)
plot(svmrad,dt.train)
svmrad.pred=predict(svmrad,dt.train)
table(svmrad.pred,dt.train$z)
```
As can be seen, in the train data, the SVM radial performs the best, then the SVM linear and then the SVM polynomial.

After that, we check all three methods on the test data and compute the test error rate.
```{r}
svc.pred2=predict(svc,dt.test)
table(svc.pred2,dt.test$z)
svmpoly.pred2=predict(svmpoly,dt.test)
table(svmpoly.pred2,dt.test$z)
svmrad.pred2=predict(svmrad,dt.test)
table(svmpoly.pred2,dt.test$z)
```
As can be seen, in the test data, the linear SVM performs the best with lowest test error rate of 12%. The other SVM perform similar with test error rates of 54%.
